Papers

### 2023-01-20 quarto/index.qmd
update

* Z. Zhang, **A. Zhang**, M. Li, and A. J. Smola<br>
	<a href="https://arxiv.org/abs/2210.03493" target="_blank">Automatic Chain of Thought Prompting in Large Language Models</a><br>
	*"Let's think not just step by step, but also one by one."*
	In *arXiv*, 2022<br>
	<a href="https://twitter.com/astonzhangAZ/status/1579489453789581312" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
	<a href="https://github.com/amazon-research/auto-cot" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

* J. Chen, **A. Zhang**, X. Shi, M. Li, A. J. Smola, and D. Yang<br>
	<a href="https://arxiv.org/abs/2301.01821" target="_blank">Parameter-Efficient Fine-Tuning Design Spaces</a><br>
	*"Don't assign the same parameter-efficient fine-tuning strategy to different layers."*
	In *arXiv*, 2022<br>
	<a href="https://twitter.com/astonzhangAZ/status/1611400421255557122" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
	<a href="https://github.com/amazon-science/peft-design-spaces" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

>>>>

* Z. Zhang, **A. Zhang**, M. Li, and A. J. Smola<br>
	<a href="https://arxiv.org/abs/2210.03493" target="_blank">Automatic Chain of Thought Prompting in Large Language Models</a><br>
	In *Proceedings of the International Conference on Learning Representations* (**ICLR**), 2023<br>
	<a href="https://twitter.com/astonzhangAZ/status/1579489453789581312" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
	<a href="https://github.com/amazon-research/auto-cot" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

* J. Chen, **A. Zhang**, X. Shi, M. Li, A. J. Smola, and D. Yang<br>
	<a href="https://arxiv.org/abs/2301.01821" target="_blank">Parameter-Efficient Fine-Tuning Design Spaces</a><br>
	In *Proceedings of the International Conference on Learning Representations* (**ICLR**), 2023<br>
	<a href="https://twitter.com/astonzhangAZ/status/1611400421255557122" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
	<a href="https://github.com/amazon-science/peft-design-spaces" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

* Z. Liu, Z. Tang, X. Shi, **A. Zhang**, M. Li, A. Shrivastava, and A. Wilson<br>
	<a href="https://arxiv.org/abs/2212.14453" target="_blank">Learning Multimodal Data Augmentation in Feature Space</a><br>
	In *Proceedings of the International Conference on Learning Representations* (**ICLR**), 2023<br>

* T. Yang, Y. Zhu, Y. Xie, **A. Zhang**, C. Chen, and M. Li<br>
	<a href="https://openreview.net/forum?id=CIoSZ_HKHS7" target="_blank">AIM: Adapting Image Models for Efficient Video Understanding</a><br>
	In *Proceedings of the International Conference on Learning Representations* (**ICLR**), 2023<br>

### 2023-01-20 quarto/papers.qmd
update

* Z. Zhang, **A. Zhang**, M. Li, and A. J. Smola<br>
<a href="https://arxiv.org/abs/2210.03493" target="_blank">Automatic Chain of Thought Prompting in Large Language Models</a><br>
*"Let's think not just step by step, but also one by one."*
In *arXiv*, 2022<br>
<a href="https://twitter.com/astonzhangAZ/status/1579489453789581312" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
<a href="https://github.com/amazon-research/auto-cot" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

* J. Chen, **A. Zhang**, X. Shi, M. Li, A. J. Smola, and D. Yang<br>
<a href="https://d2l-webdata.s3.us-west-2.amazonaws.com/papers/PEFT-design-spaces.pdf" target="_blank">Parameter-Efficient Fine-Tuning Design Spaces</a><br>
*"Don't assign the SAME parameter-efficient fine-tuning strategy to DIFFERENT layers."*
In *arXiv*, 2022<br>

@@

* Z. Liu, Z. Tang, X. Shi, **A. Zhang**, M. Li, A. Shrivastava, and A. Wilson<br>
<a href="https://arxiv.org/abs/2212.14453" target="_blank">Learning Multimodal Data Augmentation in Feature Space</a><br>
*"The first augmentation method to be applied to the joint of text, image, and tabular data."*
In *arXiv*, 2022<br>

>>>>

* Z. Zhang, **A. Zhang**, M. Li, and A. J. Smola<br>
<a href="https://arxiv.org/abs/2210.03493" target="_blank">Automatic Chain of Thought Prompting in Large Language Models</a><br>
In *Proceedings of the International Conference on Learning Representations* (**ICLR**), 2023<br>
<a href="https://twitter.com/astonzhangAZ/status/1579489453789581312" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
<a href="https://github.com/amazon-research/auto-cot" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

* J. Chen, **A. Zhang**, X. Shi, M. Li, A. J. Smola, and D. Yang<br>
<a href="https://arxiv.org/abs/2301.01821" target="_blank">Parameter-Efficient Fine-Tuning Design Spaces</a><br>
In *Proceedings of the International Conference on Learning Representations* (**ICLR**), 2023<br>
<a href="https://twitter.com/astonzhangAZ/status/1611400421255557122" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
<a href="https://github.com/amazon-science/peft-design-spaces" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

* Z. Liu, Z. Tang, X. Shi, **A. Zhang**, M. Li, A. Shrivastava, and A. Wilson<br>
<a href="https://arxiv.org/abs/2212.14453" target="_blank">Learning Multimodal Data Augmentation in Feature Space</a><br>
In *Proceedings of the International Conference on Learning Representations* (**ICLR**), 2023<br>

* T. Yang, Y. Zhu, Y. Xie, **A. Zhang**, C. Chen, and M. Li<br>
<a href="https://openreview.net/forum?id=CIoSZ_HKHS7" target="_blank">AIM: Adapting Image Models for Efficient Video Understanding</a><br>
In *Proceedings of the International Conference on Learning Representations* (**ICLR**), 2023<br>

@@
